### 2014-05-09 docs/paper.tex
Should discuss Google's visibility of the first and last hop.
Should mention Dust for traffic shaping.
Note about splitting challenges into three.
ACKs terminology "unobservability" and "unblockability."
Cite Cirripede and Routing Around Decoys.
More general decoy routing paragraph.

@@

% Lantern
% Psiphon
% Infranet
% Freegate
% Ultrasurf

@@

Decoy routing is
a recently proposed anti-blocking approach. Telex~\cite{telex}
asks friendly ISPs to deploy special software on routers between censored users and
popular, uncensored Internet destinations.
Circumvention traffic is marked with a special ``tag'' that is distinguishable from a random string only
by Telex routers (not by the censor).
On receiving such a tagged communication, the Telex router shunts it away from its apparent destination
and toward the censored destination requested by the client.
Telex is conceptually similar to our work.
Both systems use a piece of network infrastructure as a decoy to redirect certain flows
(for Telex it is an ISP router; for us it is the Google frontend server),
and both tag flows in a way that is visible only to the decoy router
(for Telex a tag is a hash embedded in the TLS client randomness;
for us it is the HTTP Host header, hidden within an HTTPS stream).
An important difference is that Telex requires some degree of buy-in from network operators
whose incentives may not be aligned with circumventors'.
We require no active participation on the part of the frontend operator,
only a lack of active opposition.

CensorSpoofer~\cite{censorspoofer}
decouples the upstream and downstream channels.
The client sends upstream data to the CensorSpoofer proxy over a low-bandwidth covert channel such as email.
At the same time, the client pretends to have an innocuous communication (such as a VoIP call) with an unblocked dummy host.
The CensorSpoofer proxy sends encrypted UDP data back downstream to the client,
protecting its true IP address by spoofing the source of all its packets
so that they appear to come from the dummy host.
From the censor's point of view, the client is carrying on a conversation only with the dummy host.
If the dummy is blocked, another can be used in its place,
as the CensorSpoofer proxy's true IP address remains unknown.
% Cirripede

% Routing around decoys
A recent study~\cite{nodirectionhome} on AS
topology suggests that defeating decoy routing is likely to be expensive for the
censors, if the decoy routers are strategically deployed. Despite that decoy
routing is a sound technical approach, it is still questionable whether ISPs are
willing to act against state-level censors. However, the takeaway is that the
censors are unwilling to completely block day-to-day Internet access, which we
can take advantage of.

@@

>>>>

% I'm thinking of recasting this as three challenges:
%  1. Content blocking.
%  2. Endpoint blocking.
%  3. Active scanning.
% We have something to say for all three and related work falls into one or
% more of those categories.
%
% "Cover your ACKs" talks about "unobservability" and "unblockability," maybe
% isomorphic to our "blocking by content" and "blocking by endpoint."

@@

% Lantern
% Psiphon
% Infranet
% Freegate
% Ultrasurf
% Dust

@@

Decoy routing~\cite{decoyrouting} is a technique that puts
proxies in the middle of network paths, rather than at the endpoints.
Realizations of the decoy routing idea include Telex~\cite{telex}
and Cirripede~\cite{cirripede}.
Decoy routing asks friendly ISPs to deploy special software on routers that lie
between censored users and uncensored Internet destinations.
Circumvention traffic is ``tagged'' in a way that is detectable only
by decoy routers, and not by the censor.
On receiving a tagged communication, the decoy router shunts it away from its apparent destination
and toward the censored destination requested by the client.
Our work is conceptually similar to decoy routing,
though the action happens at the application layer rather than the network layer.
Both systems use a piece of network infrastructure as a decoy to redirect certain flows:
in decoy routing it is an ISP router; for us it is the front domain.
Both tag flows in a way that is visible only to the decoy router:
in decoy routing a tag may be, for example, a hash embedded in the TLS client randomness;
for us it is the HTTP Host header, encrypted within an HTTPS stream.
Decoy routing generally requires the cooperation of large, centrally located
router operators,
whereas we only need to buy web application hosting.

CensorSpoofer~\cite{censorspoofer}
decouples the upstream and downstream channels.
The client sends upstream data to the CensorSpoofer proxy over a low-bandwidth covert channel such as email.
At the same time, the client pretends to have an innocuous communication (such as a VoIP call) with an unblocked dummy host.
The CensorSpoofer proxy sends encrypted UDP data back downstream to the client,
protecting its true IP address by spoofing the source of all its packets
so that they appear to come from the dummy host.
From the censor's point of view, the client is carrying on a conversation only with the dummy host.
If the dummy is blocked, another can be used in its place,
as the CensorSpoofer proxy's true IP address remains unknown.

\cite{ccs2012-decoys}
% Routing around decoys
A recent study~\cite{nodirectionhome} on AS
topology suggests that defeating decoy routing is likely to be expensive for the
censors, if the decoy routers are strategically deployed. Despite that decoy
routing is a sound technical approach, it is still questionable whether ISPs are
willing to act against state-level censors. However, the takeaway is that the
censors are unwilling to completely block day-to-day Internet access, which we
can take advantage of.

@@

\section{Security}

% Google can deanonymize you, because they are the first hop,
% and also often the last hop because of their popularity.
